A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-12-05 analysis/supplement.Rmd
feat: add confidence bands to roc plots

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, MELD 3.0, and MELD-Plus7, as described in [@blanche2013]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELD3)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD 3.0" = timeROC_MELD3,
    "MELD-Plus7" = timeROC_MELDPlus7
)
plot_surv_roc_trend(m, xlab = "time [days]", col = viridisLite::viridis(6)[-2])
```

>>>>

# ROC curves

```{r roc-cb-all, fig.width = 7, fig.height = 7, echo = FALSE, message = FALSE, fig.cap = "Receiver operating characteristic (ROC) curve. Area under the time-dependent ROC curve (AUC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, MELD 3.0, MELD-Plus7, as described in [@blanche2013]. The dashed lines depict the corresponding 95% confidence bands calculated by threshold averaging as described in [@fawcett2004]."}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELD3)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)
col <- viridisLite::viridis(6)[-2]
m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD 3.0" = timeROC_MELD3,
    "MELD-Plus7" = timeROC_MELDPlus7
)
invisible(roc <- plot_surv_roc(m, timepoint = 90, col = col, legend = FALSE))
o <- order(-roc)
ci <- attr(roc, "CI")[o]
roc <- roc[o]

rjlegend(
    legend = c(
        sprintf("AUC %s: %0.3f %s", names(roc), roc, ci),
        "95% confidence bands"
    ),
    col = c(col[o], "#808080"),
    lty = c(rep(1, length(m)), 2)
)

tar_load(confidencebands_MELD)
tar_load(confidencebands_MELDNa)
tar_load(confidencebands_MELD3)
tar_load(confidencebands_MELDPlus7)
tar_load(confidencebands_RCV)
cb <- list(
    AMELD = confidencebands_RCV,
    MELD = confidencebands_MELD,
    "MELD-Na" = confidencebands_MELDNa,
    "MELD 3.0" = confidencebands_MELD3,
    "MELD-Plus7" = confidencebands_MELDPlus7
)

for (i in seq_along(cb)) {
    lines(cb[[i]]$FP["2.5%",], cb[[i]]$TP["97.5%",], col = col[o][i], lty = 2)
    lines(cb[[i]]$FP["97.5%",], cb[[i]]$TP["2.5%",], col = col[o][i], lty = 2)
}
```

```{r roc-cb-ameld, fig.width = 7, fig.height = 7, echo = FALSE, message = FALSE, fig.cap = "Receiver operating characteristic (ROC) curve. Area under the time-dependent ROC curve (AUC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, MELD 3.0, MELD-Plus7, as described in [@blanche2013]. The dashed lines depict the corresponding 95% confidence bands for AMELD calculated by threshold averaging as described in [@fawcett2004]. The other confidence bands are hidden for easier readability."}
invisible(plot_surv_roc(m, timepoint = 90, col = col, legend = FALSE))
j <- which(m[["AMELD"]]$times == 90)
#lines(m[["AMELD"]]$FP[, j], m[["AMELD"]]$TP[, j], col = col[1], lty = 1, lwd = 2)
rjlegend(
    legend = c(
        sprintf("AUC %s: %0.3f %s", names(roc), roc, ci),
        "95% confidence bands"
    ),
    col = c(col[o], "#808080"),
    lty = c(rep(1, length(m)), 2)
)
lines(cb[["AMELD"]]$FP["2.5%",], cb[["AMELD"]]$TP["97.5%",], col = col[1], lty = 2)
lines(cb[["AMELD"]]$FP["97.5%",], cb[["AMELD"]]$TP["2.5%",], col = col[1], lty = 2)
polygon(
    c(cb[["AMELD"]]$FP["2.5%",], rev(cb[["AMELD"]]$FP["97.5%",])),
    c(cb[["AMELD"]]$TP["97.5%",], rev(cb[["AMELD"]]$TP["2.5%",])),
    col = sub("FF$", "11", col[1]), lty = 0
)
```

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, fig.cap = "Trend in the area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na, MELD 3.0, and MELD-Plus7, as described in [@blanche2013]."}
plot_surv_roc_trend(m, xlab = "time [days]", col = viridisLite::viridis(6)[-2])
```
